---
title: "BayesianSurvival"
author: "Josephine Hillebrand Hansen"
date: "22/05/2020"
output: html_document
---

#Creating a dataset of when each NAMED character goes to die
https://listofdeaths.fandom.com/wiki/Game_of_Thrones
```{r}
library(quanteda)
data = read.csv("deaths_scraped.txt", header = FALSE, sep = "\n", stringsAsFactors = FALSE)

season = list()
season_name = list()

for (i in (1:nrow(data))){
  data$V1[i] = char_tolower(data$V1[i])
  if (grepl("season", data$V1[i]) & grepl("edit", data$V1[i])){
    season = append(season, i)
    season_name = append(season_name, gsub("edit", "", data$V1[i]))}
}

season = unlist(season)
season_name = unlist(season_name)


#Create df
df <- data.frame(matrix(ncol = 2, nrow = nrow(data)))
x <- c("Season", "Death")
colnames(df) <- x


#Create df with episodes
for (i in (1:length(season))){
  if (i == length(season)){
    df$Season[season[i]:length(df$Season)] = season_name[i]
    for (j in (season[i]:nrow(data))){
      df$Death[j] = data$V1[j]
    }
  }
  else{
    df$Season[season[i]:season[i+1]] = season_name[i]
    
    for (j in (season[i]:season[i+1])){
      df$Death[j] = data$V1[j]
    }
      
  }
}


#Remove all season from the Death row
for (i in (1:nrow(df))){
  if (grepl("season", df$Death[i]) & grepl("edit", df$Death[i])){
    df = df[-i,]
  }
}


#Repeat for episode, and split up data by who died, and what happened

episode = list()
episode_name = list()

for (i in (1:nrow(df))){
  if (grepl("edit", df$Death[i])){
    episode = append(episode, i)
    episode_name = append(episode_name, gsub("edit", "", df$Death[i]))}
}

episode = unlist(episode)
episode_name = unlist(episode_name)



deaths <- data.frame(matrix(ncol = 4, nrow = nrow(df)))
x <- c("Season", "Episode", "Name", "How")
colnames(deaths) <- x
deaths$Season = df$Season


#Create df with episodes
for (i in (1:length(episode))){
  if (i == length(episode)){
    deaths$Episode[episode[i]:nrow(deaths)] = episode_name[i]
    for (j in (episode[i]:nrow(deaths))){
      deaths$Name[j] = sub("\\s\\-.*", "", df$Death[j])
      deaths$How[j] = sub(".*?\\-\\s", "", df$Death[j])
    }
  }
  else{
    deaths$Episode[episode[i]:episode[i+1]] = episode_name[i]
    
    for (j in (episode[i]:episode[i+1])){
      deaths$Name[j] = sub("\\s\\-.*", "", df$Death[j])
      deaths$How[j] = sub(".*?\\-\\s", "", df$Death[j])
    }
      
  }
}



#Remove episodes from the rows
for (i in (1:nrow(deaths))){
  if (grepl("edit", deaths$Name[i])){
    deaths = deaths[-i,]
  }
}


#Clean up and remove titles
titles = c("lord ", "ser ", "queen ", "lady ", "prince ", "king ", " \\(the hound\\)", " \\(the mountain\\)", " \\(the kingslayer\\)", "the high ", "commander ", " the", "ned ", "master ", "the ", " seaworth", " halfhand", " xhoan daxos", "mo ullhor", " hollard", " kenning", " hill", " reed", " rayder", "first steward ", "first builder ", " tully", " lemoncloak", " paenymion", " of myr", " \\(littlefinger\\)", " strickland")

for (title in titles){
  for (i in (1:nrow(deaths))){
    deaths$Name[i] = gsub(title, "", deaths$Name[i])
  }}

for (i in (1:nrow(deaths))){
  if (deaths$Name[i] == "stableboy"){
    deaths$Name[i] = "stable boy"}
  if (deaths$Name[i] == "amory lorch"){
    deaths$Name[i] = "amory"
  }
  if (deaths$Name[i] == "alton lannister"){
    deaths$Name[i] = "alton"
  }
  if (deaths$Name[i] == "winterfell shepard"){
    deaths$Name[i] = "winterfell shepherd"
    }
  if (deaths$Name[i] == "jack"){
    deaths$Name[i] = "jacks"
  }
  if (deaths$Name[i] == "lorren"){
    deaths$Name[i] = "black lorren"
  }
  if (deaths$Name[i] == "willem lannister"){
    deaths$Name[i] = "willem"
    }
  if (deaths$Name[i] == "martyn lannister"){
    deaths$Name[i] = "martyn"
  }
  if (deaths$Name[i] == "talisa stark"){
    deaths$Name[i] = "talisa"
  }
  if (deaths$Name[i] == "wendel manderly"){
    deaths$Name[i] = "manderly"
  }
  if (deaths$Name[i] == "olly's mother"){
    deaths$Name[i] = "ollys mother"
  }
  if (deaths$Name[i] == "mole's town whore"){
    deaths$Name[i] = "moles town whore"
  }
  if (deaths$Name[i] == "princess shireen baratheon"){
    deaths$Name[i] = "shireen"
  }
  if (deaths$Name[i] == "selyse baratheon"){
    deaths$Name[i] = "selyse"
  }
  if (deaths$Name[i] == "princess myrcella baratheon"){
    deaths$Name[i] = "selyse"
  }
  if (deaths$Name[i] == "areo hotah"){
    deaths$Name[i] = "areo"
  }
  if (deaths$Name[i] == "doran martell"){
    deaths$Name[i] = "doran"
  }
  if (deaths$Name[i] == "trystane martell"){
    deaths$Name[i] = "trystane"
  }
  if (deaths$Name[i] == "walda bolton"){
    deaths$Name[i] = "walda"
  }
  if (deaths$Name[i] == "balon greyjoy"){
    deaths$Name[i] = "balon"
  }
  if (deaths$Name[i] == "allithorne"){
    deaths$Name[i] = "alliser thorne"
  }
  if (deaths$Name[i] == "three eyed raven"){
    deaths$Name[i] = "threeeyed raven"
  }
  if (deaths$Name[i] == "brother ray"){
    deaths$Name[i] = "ray"
  }
  if (deaths$Name[i] == "wun weg wun dar wun"){
    deaths$Name[i] = "wun wun"
  }
  if (deaths$Name[i] == "lothar frey"){
    deaths$Name[i] = "lothar"
  }
  if (deaths$Name[i] == "black walder rivers"){
    deaths$Name[i] = "black walder"
  }
  if (deaths$Name[i] == "obara sand"){
    deaths$Name[i] = "obara"
    }
  if (deaths$Name[i] == "nymeria sand"){
    deaths$Name[i] = "nymeria"
    }
  if (deaths$Name[i] == "tyene sand"){
    deaths$Name[i] = "sand"
  }
  if (deaths$Name[i] == "randyll tarly"){
    deaths$Name[i] = "randyll"
  }
  if (deaths$Name[i] == "dickon tarly"){
    deaths$Name[i] = "dickon"
  }
  if (deaths$Name[i] == "ellaria sand"){
    deaths$Name[i] = "ellaria"
  }
  if (deaths$Name[i] == "of bones"){
    deaths$Name[i] = "lord of bones"
  }
  if (deaths$Name[i] == "crane"){
    deaths$Name[i] = "lady crane"
  }
}

```


#check how many of the characters we know die say something
```{r}
data = read.csv("game-of-thrones-script-all-seasons/got_cleaned.csv",stringsAsFactors = FALSE)

list_of_characters = unique(data$Name)


deaths$Speaks <- NA

i = 0
for (name in deaths$Name){
  if (!(name %in% list_of_characters)){
    i = i+1
  }
  else{
    deaths$Speaks[i] = 1
  }
}

for (i in (1:nrow(deaths))){
  if (!(deaths$Name[i] %in% list_of_characters)) {
    deaths$Speaks[i] = 0
  }
  else {
    deaths$Speaks[i] = 1
  }
}

deaths <- transform(deaths, id=match(Episode, unique(Episode)))


```

#Add sentiment scores
```{r}
library(sentimentr)

mytext <- data$lemma
mytext <- get_sentences(mytext)
sent_scor <- as.data.frame(sentiment(mytext))

data$Sentiment <- sent_scor$sentiment

```


```



#Find out when characters first appears, last appears etc.
```{r}
data <- transform(data, id=match(Episode.Title, unique(Episode.Title)))


library(dplyr)

apperance = data %>%
  group_by(Name) %>%
  summarize(first_apperance = min(id),
            
            last_apperance = ifelse(max(id) > 67, 67, max(id)),
            
            total_apperance = ifelse(!("Season 8" %in% unique(Season)), length(unique(id)), sum(unique(id)< 68)),
            
            seasons_apperance = ifelse(!("Season 8" %in% unique(Season)), length(unique(Season)), length(unique(Season))-1),
            
            time_of_monitoring = last_apperance-first_apperance+1,
            
            Prominence = (total_apperance/time_of_monitoring)*seasons_apperance,
            
            Sentiment = mean(Sentiment))


#Merge first_apperance with deaths
df.merge <- merge(x = apperance, y = deaths, by = "Name", all.x = TRUE)


```

#Fix some names
```{r}

allegiance <- read.csv("bayesianGameofThrones-master/char_final.csv", stringsAsFactors = FALSE)
allegiance <- allegiance[-1:-3,]
allegiance$Name <- char_tolower(allegiance$Name)


for (k in (1:nrow(df.merge))){
  if (!(df.merge$Name[k] %in% allegiance$Name)){
    name = df.merge$Name[k]
    #print(name)
    for (i in (1:nrow(allegiance))){
      if (name == sub('\\s.*', '', allegiance$Name[i])){
        df.merge$Name[k] = allegiance$Name[i]
      }
      if (sub('lord', '', name) == sub('\\s.*', '', allegiance$Name[i])){
        df.merge$Name[k] = allegiance$Name[i]
      }
      if (sub('knight', '', name) == sub('\\s.*', '', allegiance$Name[i])){
        df.merge$Name[k] = allegiance$Name[i]
      }
      if (sub('lady', '', name) == sub('\\s.*', '', allegiance$Name[i])){
        df.merge$Name[k] = allegiance$Name[i]
      }
      if (sub('king', '', name) == sub('\\s.*', '', allegiance$Name[i])){
        df.merge$Name[k] = allegiance$Name[i]
      }
      if (sub('lord', '', name) == allegiance$Name[i]){
        df.merge$Name[k] = allegiance$Name[i]
      }
      if (sub('knight', '', name) == allegiance$Name[i]){
        df.merge$Name[k] = allegiance$Name[i]
      }
      if (sub('lady', '', name) == allegiance$Name[i]){
        df.merge$Name[k] = allegiance$Name[i]
      }
      if (sub('king', '', name) == allegiance$Name[i]){
        df.merge$Name[k] = allegiance$Name[i]
      }}
      }
}
```


#Merge with Df showing allegiance and so on - BASED ON BOOKS
```{r}



df.merge <- merge(x = df.merge, y = allegiance, by = "Name")#, all.x = TRUE)
```


#Clean up the columns we don't need and rename others to something that makes sense
```{r}
df.merge$DwD <- NULL
df.merge$FfC <- NULL
df.merge$SoS <- NULL
df.merge$CoK <- NULL
df.merge$GoT <- NULL
df.merge$Book.Death.Percentage <- NULL
df.merge$Book.Intro.Chapter <- NULL
df.merge$Book.of.Death <- NULL
df.merge$Death.Year <- NULL
df.merge$Speaks <- NULL
df.merge$Death.Chapter <- NULL
df.merge$Episode.x <- NULL

library(tidyverse)
df <- df.merge %>%
  rename(
    episode_of_death = id
  )
#Remove rows 11 and 13 containing misspelled duplicate
#df = df[-13:-14,]
#df = df[-11,]


```



#Adding survival status
```{r}
#Add df with whether they have died or not
df$Dead = NA

for (i in 1:nrow(df)){
  if (is.na(df$episode_of_death[i])){
    df$Dead[i] = 0
  }
  else{
    df$Dead[i] = 1
  }
} # 1 = dead

#Create subset only containing characters being introduced before season 8
df = subset(df, first_apperance < 68)

#Set characters who died later to still be alive
df_survival = df
for (i in (1:nrow(df_survival))){
  print(df_survival$Name[i])
  if (df_survival$episode_of_death[i] > 67 | is.na(df_survival$episode_of_death[i])) {
    print(df_survival$Name[i])
    
    df_survival$episode_of_death[i] = NA
    df_survival$Dead[i] = 0
  }
  else{
    
  }}


write.csv(df_survival, file = "survival.csv")


```







#Loading packages for survival analysis

```{r}
library(survival)
library(ranger)
library(ggplot2)
library(dplyr)
library(ggfortify)
library(survminer)

```





#For the GOT-data
```{r}
GOT <- read.csv("C:/Users/hille/Desktop/Data science/Project/A-Game-of-Data---Data-Science-Exam-Project/survival.csv")

#Remove characters we have twice in the data due to our merging of names
unique_names = unique(GOT$Name)

new = GOT
for (name in unique_names){
  if (length(GOT$Name[GOT$Name == name]) > 1){
    if (sum(GOT$Dead[GOT$Name == name]) == 1){
      new = new[!(new$Name == name & new$Dead == 0),]
    }
  else {
    if (GOT$Prominence[GOT$Name == name][1] > GOT$Prominence[GOT$Name == name][2]){
      prom = GOT$Prominence[GOT$Name == name][2]
      new = new[!(new$Name == name & new$Prominence == prom),] 
      }
    else {
      prom = GOT$Prominence[GOT$Name == name][1]
      new = new[!(new$Name == name & new$Prominence == prom),]
    }
    
  }
}}

GOT <- new

#Set nobility and gender as factors
GOT$Nobility <- as.factor(GOT$Nobility)
#GOT$Dead <- as.factor(GOT$Dead)
GOT$Gender <- as.factor(GOT$Gender)
#GOT$Time = NA

#More data cleaning
GOT$Allegiances = gsub("House ", "", GOT$Allegiances)

GOT$Dead[GOT$Name == "jon snow"] = 0


#Change minor houses to be allegiant with "other"
minor_houses <- c("Arryn", "Greyjoy", "Martell", "Tully", "Tyrell", "Wildling")
for (house in minor_houses){
  GOT$Allegiances[GOT$Allegiances == house] <- "Other"}
  
  
write.csv(GOT, file = "survival.csv")


```


Kaplan-Meier estimates of survival probability
```{r}
#Produce Kaplan-Meier estimates of probability of survival over time
km_fit_GOT <- survfit(Surv(time_of_monitoring, Dead) ~ 1, data = GOT)
summary(km_fit_GOT, times = c(1*(1:10),66,67))

autoplot(km_fit_GOT) +
  xlab("Episodes since introduction") +
  ylab("Probability of surviving")

```


#Aalen plot of how covariates changes over tiem
```{r}
#How covariates change over time
aa_fit <-aareg(Surv(time_of_monitoring, Dead) ~ Nobility + Gender + Allegiances, 
                 data = GOT)
aa_fit
autoplot(aa_fit)



```



#Plots
Distribution of time to death
```{r}

ggplot(data = transform(GOT, Nobility = c("Commonfolk", "Noble")), aes(x = time_of_monitoring, fill = Dead)) + 
  geom_histogram() + 
  facet_grid(Nobility ~.) + 
  ggtitle("Distribution of time to censoring and death by nobility status") +
  xlab("Episodes since introduction") +
  ylab("Count")  +
  scale_fill_discrete(breaks=c("0", "1"),
                      labels=c("Censored", "Death/uncensored"))
                      
                      
                      
ggplot(data = GOT, aes(x = time_of_monitoring, fill = as.factor(Dead))) + 
  geom_histogram() + 
  facet_grid(Nobility ~.) + 
  ggtitle("Distribution of time to censoring and death by nobility status") +
  xlab("Episodes since introduction") +
  ylab("Count")  +
  scale_fill_discrete(breaks=c("0", "1"),
                      labels=c("Censored", "Death/uncensored"))

```



#Cox proportional hazard model comparisons
```{r}
GOT_FIT_OTHERS <- coxph(Surv(time_of_monitoring, Dead) ~ Nobility + Gender + Allegiances, data = GOT)
GOT_FIT_OURS <- coxph(Surv(time_of_monitoring, Dead) ~ Sentiment, data = GOT)
GOT_FIT_COMBINED <- coxph(Surv(time_of_monitoring, Dead) ~ Nobility + Gender + Allegiances + Sentiment, data = GOT)

ggforest(GOT_FIT_OTHERS, data = GOT)
ggforest(GOT_FIT_OURS, data = GOT)
ggforest(GOT_FIT_COMBINED, data = GOT)



```


#Check if proportional hazard assumptions of chosen model are ignored
Test is not significant = Covariates do not vary significantly over time
```{r}
cz <- cox.zph(GOT_FIT_OTHERS)
print(cz) #NOT SIGNIFICANT - YAY




```



#Plot the cox model against the KM
```{r}
cox_fit <- survfit(GOT_FIT_OTHERS)
coxi <- rep("Cox",length(cox_fit$time))
cox_df <- data.frame(cox_fit$time,cox_fit$surv,coxi)
names(cox_df) <- c("Time","Surv","Model")


km_fit <- survfit(Surv(time_of_monitoring, Dead) ~ 1, data = GOT)


kmi <- rep("KM",length(km_fit$time))
km_df <- data.frame(km_fit$time,km_fit$surv,kmi)
names(km_df) <- c("Time","Surv","Model")

plot_df <- rbind(km_df,cox_df)

p <- ggplot(plot_df, aes(x = Time, y = Surv, color = Model))
p + geom_line()



autoplot(cox_fit)
```





#Finding proportional hazard for each character
```{r}
#This gives us a prediction of how much at risk each character is compared to the baseline
risk = as.data.frame(predict(GOT_FIT_OTHERS, GOT, type="risk", se.fit = TRUE))
risk$Name = GOT$Name
risk$time = GOT$time_of_monitoring
risk$status = GOT$Dead
risk$season_8 = NA
risk$last = GOT$last_apperance


```




#Extrapolate data to predict how characters will fare in season 8
```{r}
GOT_FIT_OTHERS
summary(GOT_FIT_OTHERS)

#Convert our probability estimates to a survival object - i.e. estimates of probability of surviving
cox_fit <- survfit(GOT_FIT_OTHERS)
surv <- cox_fit$surv
df <- as.data.frame(surv)
df$time <- cox_fit$time

#Fit exponential model to the data
theta.0 <- min(df$surv) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(surv - theta.0) ~ time, data=df)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

#Fit exponential model
model <- nls(surv ~ alpha * exp(beta * time) + theta , data = df, start = start)



plot(df$time, df$surv)
lines(df$time, predict(model, list(x = df$time)), col = 'skyblue', lwd = 3)



#create predictions for probability of surviving up to 73 episodes after introduction

newdata <- data.frame(
  time = c(1:73)
)

model_preds = predict(model, newdata = newdata)

#Now that we have our predictions, we can calculate the probability of surviving an additional six episodes for each character still alive by season 7

#and now we just need to calculate probabilities for each person dependent on how long they have been in the show and their individual probabilities


for (i in (1:nrow(GOT))){
  if (risk$status[i] == 1){
    risk$season_8[i] = 0
  }
  else if (risk$last[i] < 67) {
    risk$season_8[i] = 0}
  else {
    risk$season_8[i] = (1-model_preds[risk$time[i]+6]/model_preds[risk$time[i]])*risk$fit[i]
  }
}


```

